\documentclass[../main/NEMO_manual]{subfiles}

\begin{document}

% ================================================================
% Abstract
% ================================================================

\chapter*{Abstract}

\vspace{-40pt}

{\small
  The ocean engine of NEMO (Nucleus for European Modelling of the Ocean) is a primitive equation model adapted to
  regional and global ocean circulation problems.
  It is intended to be a flexible tool for studying the ocean and its interactions with
  the others components of the earth climate system over a wide range of space and time scales.
  Prognostic variables are the three-dimensional velocity field, a non-linear sea surface height,
  the \textit{Conservative} Temperature and the \textit{Absolute} Salinity.
  In the horizontal direction, the model uses a curvilinear orthogonal grid and in the vertical direction,
  a full or partial step $z$-coordinate, or $s$-coordinate, or a mixture of the two.
  The distribution of variables is a three-dimensional Arakawa C-type grid.
  Various physical choices are available to describe ocean physics, including TKE, and GLS vertical physics.
  Within NEMO, the ocean is interfaced with a sea-ice model (LIM or CICE),
  passive tracer and biogeochemical models (TOP) and,
  via the OASIS coupler, with several atmospheric general circulation models.
  It also support two-way grid embedding via the AGRIF software.
} 

% ================================================================
% Disclaimer
% ================================================================
\chapter*{Disclaimer}

Like all components of NEMO,
the ocean component is developed under the \href{http://www.cecill.info/}{CECILL license},
which is a French adaptation of the GNU GPL (General Public License).
Anyone may use it freely for research purposes,
and is encouraged to communicate back to the NEMO team its own developments and improvements.
The model and the present document have been made available as a service to the community.
We cannot certify that the code and its manual are free of errors.
Bugs are inevitable and some have undoubtedly survived the testing phase.
Users are encouraged to bring them to our attention.
The author assumes no responsibility for problems, errors, or incorrect usage of NEMO.

\vspace{1cm}
NEMO reference in papers and other publications is as follows:
\vspace{0.5cm}

Madec, G., and the NEMO team, 2008: NEMO ocean engine. 
\textit{Note du P\^ole de mod\'{e}lisation}, Institut Pierre-Simon Laplace (IPSL), France, 
No 27, ISSN No 1288-1619.\\


\vspace{0.5cm}
Additional information can be found on \href{http://www.nemo-ocean.eu/}{www.nemo-ocean.eu}.
\vspace{0.5cm}

\biblio

\end{document}
